Preprocessing

### 2017-07-23 preprocessing.Rmd
run 2 or 4

```{r}
{{G@code <- bigsnpr:::CODE_IMPUTE_PRED}}
big_counts(G, ind.col = 1:10)
```

>>>>

```{r}
# You need to change the code of G
G@code <- bigsnpr:::CODE_IMPUTE_PRED
big_counts(G, ind.col = 1:10)
```

```{r}
# To make this permanent, you need to save (modify) the file on disk
celiac$genotypes@code <- bigsnpr:::CODE_IMPUTE_PRED
saveRDS(celiac, "backingfiles/celiacQC.rds")
```
